### 2018-12-21 reports/thesis/chapters/5_inference.tex
Added real data in inference chapter

>>>>

\subsection{Real Data}

\begin{figure}[htp]
	\centering
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1_z.eps}
				\caption{$r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1.txt}$}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2_z.eps}
				\caption{$r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2.txt}$}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3_z.eps}
				\caption{$r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3.txt}$}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4_z.eps}
				\caption{$r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4.txt}$}
			\end{subfigure}
		}
	\caption{Filtered $z$ image from the \texttt{Sep16 120deg} dataset. Various kernel radiuses were used.}
	\label{fig:inference_sep16120deg_zfiltered}
\end{figure}

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1_sig.eps}
				\caption{Image with sig.~pixels}
			\end{subfigure}
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1_logp.eps}
				\caption{$-\log p$}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1_nullMean.eps}
				\caption{Empirical null mean}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1_nullStd.eps}
				\caption{Empirical null std}
			\end{subfigure}
		}
	\caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1.txt}$. a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level. b) $p$-values on the log scale. c) and d) Empirical null mean and std.}
	\label{fig:inference_sep16120deg_inference_radius1}
\end{figure}

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2_sig.eps}
				\caption{Image with sig.~pixels}
			\end{subfigure}
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2_logp.eps}
				\caption{$-\log p$}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2_nullMean.eps}
				\caption{Empirical null mean}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2_nullStd.eps}
				\caption{Empirical null std}
			\end{subfigure}
		}
	\caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius2.txt}$. a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level. b) $p$-values on the log scale. c) and d) Empirical null mean and std.}
	\label{fig:inference_sep16120deg_inference_radius2}
\end{figure}

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3_sig.eps}
				\caption{Image with sig.~pixels}
			\end{subfigure}
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3_logp.eps}
				\caption{$-\log p$}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3_nullMean.eps}
				\caption{Empirical null mean}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3_nullStd.eps}
				\caption{Empirical null std}
			\end{subfigure}
		}
	\caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius3.txt}$. a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level. b) $p$-values on the log scale. c) and d) Empirical null mean and std.}
	\label{fig:inference_sep16120deg_inference_radius3}
\end{figure}

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4_sig.eps}
				\caption{Image with sig.~pixels}
			\end{subfigure}
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4_logp.eps}
				\caption{$-\log p$}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4_nullMean.eps}
				\caption{Empirical null mean}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4_nullStd.eps}
				\caption{Empirical null std}
			\end{subfigure}
		}
	\caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius4.txt}$. a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level. b) $p$-values on the log scale. c) and d) Empirical null mean and std.}
	\label{fig:inference_sep16120deg_inference_radius4}
\end{figure}

The empirical null filter was applied to the \texttt{Sep16 120deg} image as shown at the start of the chapter. Figure \ref{fig:inference_sep16120deg_zfiltered} shows the filtered $z$ images for various kernel radiuses. For $r=\addNumber{../figures/inference/defectdetect/ExperimentDefectDetectSep16120deg_radius1.txt}$, the resulting $z$ image is smooth and treated everything as the null. When a large enough radius was used, the defects are highlighted by the higher $z$ statistics and everything else remain unchanged. Figures \ref{fig:inference_sep16120deg_inference_radius1} to \ref{fig:inference_sep16120deg_inference_radius4} shows the resulting inference along with the empirical null parameters. The figures shows that for large enough kernel radius, the filter irons out the false positives observed at the start of this chapter. All of the defects were successfully highlighted by the hypothesis test.

False positives were detected on the bottom right of the 3D printed sample. This is the result of the null distribution being bimodal where each face has a different distribution. Figure \ref{fig:inference_cornerSelect} illustrates this. The geometry of the faces and the kernel is such it results in one of the faces to be treated as non-null and then tested positive, falsely so.

\begin{figure}[htp]
	\centering
		\centerline{
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/cornerSelect.png}
				\caption{$z$ image with kernel of radius $r=120$}
			\end{subfigure}
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/cornerSelectHisto.png}
				\caption{Histogram of $z$ in the kernel}
			\end{subfigure}
		}
	\caption{A kernel of radius $r=120$ is placed over the bottom right of a unfiltered $z$ image. The histogram of the $z$ statistics captured by the kernel shows a bimodal distribution.}
	\label{fig:inference_cornerSelect}
\end{figure}

The false positives were tackled by manually segmenting the image further as shown in Figure \ref{fig:inference_segmentFurther}. It was segmented using the edges of the projection of the 3D printed object. The empirical null filter was then used on each segment independently, ignoring pixels outside the segment the filter is working on. The resulting filtered segments were stitched together to form the resulting filtered image. By using this method, the resulting inference is shown in Figure \ref{fig:inference_subroisep16120deg_inference_radius4}. It can be seen that the empirical null mean does change face to face, resulting in a clear boundary set by the edges. Most of false positives around the corners and edges have been eliminated.

\begin{figure}[htp]
	\centering
	\includegraphics[width=0.49\textwidth]{../figures/inference/defectdetect/segment.JPG}
	\caption{The $z$ was segmented further into 7 segments.}
	\label{fig:inference_segmentFurther}
\end{figure}

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentSubRoiDefectDetectSep16120deg_radius4_sig.eps}
				\caption{Image with sig.~pixels}
			\end{subfigure}
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentSubRoiDefectDetectSep16120deg_radius4_logp.eps}
				\caption{$-\log p$}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentSubRoiDefectDetectSep16120deg_radius4_nullMean.eps}
				\caption{Empirical null mean}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectdetect/ExperimentSubRoiDefectDetectSep16120deg_radius4_nullStd.eps}
				\caption{Empirical null std}
			\end{subfigure}
		}
	\caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\addNumber{../figures/inference/defectdetect/ExperimentSubRoiDefectDetectSep16120deg_radius4.txt}$. a) Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level. The $z$ statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and std.}
	\label{fig:inference_subroisep16120deg_inference_radius4}
\end{figure}
